---
title: "HMW3"
format: html
editor: visual
---

## Task 1: Control Flow Practice

Code to read the data from hmw2

```{r}

load("hw2_list.rda")

```

**1** - Creating a new column status in each dataframe

```{r}

bp_list$treatment$status <- character(nrow(bp_list$treatment))
bp_list$placebo$status <- character(nrow(bp_list$placebo))

```

**2** - I created the for loop and used the if/then/else logic to create the values inside the column status for the treatment data frame

```{r}

for (i in 1:nrow(bp_list$treatment)) {
  if (bp_list$treatment$post_bp[i] <= 120) {
    bp_list$treatment$status[i] <- "optimal"
  } else if (bp_list$treatment$post_bp[i] > 120 && bp_list$treatment$post_bp[i] <= 130) {
    bp_list$treatment$status[i] <- "borderline"
  } else {
    bp_list$treatment$status[i] <- "high"
  }
}

```

**3** - I created the for loop and used the if/then/else logic to create the values inside the column status for the placebo data frame

```{r}

for (i in 1:nrow(bp_list$placebo)) {
  if (bp_list$placebo$post_bp[i] <= 120) {
    bp_list$placebo$status[i] <- "optimal"
  } else if (bp_list$placebo$post_bp[i] > 120 && bp_list$placebo$post_bp[i] <= 130) {
    bp_list$placebo$status[i] <- "borderline"
  } else {
    bp_list$placebo$status[i] <- "high"
  }
}

```

## Task 2: Function Writing

Here I'm just following the steps to create the function from the hmw. At the end I combined the result into a named vector to store all six values and then assigned meaningful names to each value in the vector.

```{r}

stats_function <- function(data_list, stat = "mean") {

  my_fun <- get(stat)
  
  df_treatment <- data_list$treatment
  df_placebo <- data_list$placebo
  
  pre_treatment <- my_fun(df_treatment$pre_bp)
  post_treatment <- my_fun(df_treatment$post_bp)
  diff_treatment <- my_fun(df_treatment$diff_bp)

  pre_placebo <- my_fun(df_placebo$pre_bp)
  post_placebo <- my_fun(df_placebo$post_bp)
  diff_placebo <- my_fun(df_placebo$diff_bp)
  
  stats_result <- c(pre_treatment, post_treatment, diff_treatment, 
              pre_placebo, post_placebo, diff_placebo)
  
  names(stats_result) <- c("pre_treatment", "post_treatment", "diff_treatment",
                     "pre_placebo", "post_placebo", "diff_placebo")
  
  return(stats_result)
}
```

Now using the function but not specifying the mean and specifying the variance, standard deviation, minimum and maximum. This will compute the values with how many dataframes we want.

```{r}

stats_mean <- stats_function(bp_list)

stats_var <- stats_function(bp_list, "var")
stats_sd <- stats_function(bp_list, "sd")
stats_min <- stats_function(bp_list, "min")
stats_max <- stats_function(bp_list, "max")

```